GOV 1006: Milestone 5

### 2020-04-28 Milestones/miletsone5.Rmd
organizing my repo

---
title: "GOV 1006: Milestone 6"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "4/3/2020"
abstract: "Bauer (2018) finds that there is no consistent relationship between unemployment and one's trust in government and their satisfaction with democracy. I was able to completely replicate the majority of his findings aside from a summary table of the data. My extension evaluates how consistent or long-term unemployment may impact one's views. Rather than examining the effects of just a single year of unemployment, as Bauer did, I track unemployement trends over longer periods of time to see if extended periods of unemployment have a stronger impact on one's feelings towards the government and its institutions."
output: 
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
document_class: article
bibliography: milestone5_bib.bib
---

@@

library(rsconnect)
library(stargazer)
library(plyr)
library(plm)
library(wfe)
library(tidyverse)
```

```{r data}

@@

The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018). ^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0) and the published paper is availabe through [bookdown](https://bookdown.org/pquinton/milestone6/milestone6.pdf).] It was authored by Paul C. Bauer in 2018. The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general. Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.

I the appendix, I provide five replicated tables from the original publication. Of the five, Tables 1,3,4,5 were all replicable with no discrepencies. However, my replication of Table 2, did not completely match that of the paper. In reviewing the source code for Bauer's paper, it appears as though he inputs that table from another source. In his replication material, I can find where Bauer creates each of the other tables but not Table 2. Nonetheless, I attempted to replicate the table and largely suceeded. There were two variations between our tables. Bauer's table lists the absence of results for the SHP Life Satisfaction survey in 2010 whereas I have results and his lists the presence of results for the SHP Satisfaction with democracy survey in 2012 whereas in mine that is absent. These discrepencies need to be explored further.

## Extension

The fundamental motivation beyond Bauer’s paper is to study how unemployment affects trust in government and satisfaction in democracy. The goal of my extension to provide further insights and clarity into that relationship.

Because Bauer's paper utilizes panel data, it tracks households across time, providing an opportunity to analyze multi-year changes. In his conclusion, Bauer discusses the limitations of the paper and a desire to explore how the effects may differ for people experiencing long-term versus short-term unemployment. Though Bauer, correctly, ackowledges more data is needed to robustly analysize long-term verus short-term unemployment, I decided to utlize the data provided to get a sense of the relationship.

My aim was to analyze the data and identify households with multi-year unemployment reports or consistent, though not continuous, reports of unemployment across a period of time. By identifying these households, I intended to test how their unemployment experiences effected their views on democracy and the government and compare that to households with singular reports of unemployment and households without unemployment. My hypothesis was in line with Bauer’s. I predicted that households experiencing long-term or more frequent unemployment may feel more disheartened with the current state of government than households with a single year of unemployment or households without unemployment.

To actually conduct the extension, I created a new variable indicating whether someone had been unemployed the year before, lagged unemployment. I added the lagged unemployment variable to the regressions conducted by Bauer as an interaction with unemployment. The coefficient on the interaction term represents a household with unemployment in the present year and in the year before. The interaction coefficient is the one I am most interested in. As Bauer did, I ran three sets of linear regressions with the added lagged unemployment term: a standard pooled model, a fixed effects model, and a weighted fixed effects model.

```{r extension}

liss_2.0 <- liss %>%
  group_by(unit) %>%
  summarize(total_unemployment = sum(unemployed))

liss_3.0 <- liss %>%
  filter(time == 2014) %>%
  inner_join(liss_2.0, by = "unit")

modelExtension_1 <- lm(trust_in_government ~ unemployed + age + education + member, data = liss_3.0)

liss <- liss %>%
  group_by(unit) %>%
  arrange(time) %>%
  mutate(lagged_unemployed = lag(unemployed)) %>%
  ungroup(unit)

shp_2.0 <- shp %>%
  group_by(unit) %>%
  summarize(total_unemployment = sum(unemployed))

shp <- shp %>%
  group_by(unit) %>%
  arrange(time) %>%
  mutate(lagged_unemployed = lag(unemployed)) %>%
  ungroup(unit)

```

```{r tableExtension, results = 'asis'}

# SHP
# The same process as above but I used a fixed effects model instead of a pooled model
# The only difference is I change model from "pooled" to "within"

shp.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

# LISS
# Same as for SHP but with the LISS data

liss.fit.fe.tig.ext <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd.ext <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls.ext <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.tig.ext <- plm(trust_in_government ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.swd.ext <- plm(satisfaction_with_democracy ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.ls.ext <- plm(life_satisfaction ~ unemployed * lagged_unemployed + age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

# Stargazer output with the same formatting as Table 3

stargazer(shp.fit.fe.tig.ext, shp.fit.fe.control.tig.ext, shp.fit.fe.swd.ext, shp.fit.fe.control.swd.ext, shp.fit.fe.ls.ext, shp.fit.fe.control.ls.ext, liss.fit.fe.tig.ext, liss.fit.fe.control.tig.ext, liss.fit.fe.swd.ext, liss.fit.fe.control.swd.ext, liss.fit.fe.ls.ext, liss.fit.fe.control.ls.ext,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-5",
          column.sep.width = "-7.5pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models with lagged unemployment",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"),
          covariate.labels = c("Unemployed", "Lagged Unemployed", "Unemployed:Lagged Unemployed", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```

```{r table1, results='asis'}

@@

```{r table2,results='asis'}

# I begin with the LISS data
# I go through each column and classify whether there was a response or not (- for response and
# blank for NA)
# I summarize to calculate which years there were no responses for a given survey question
# I spread the data to get the years as columns

liss_2 <- liss %>%
  select(time, trust_in_government, satisfaction_with_democracy, life_satisfaction, unemployed) %>%
  mutate_at(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "unemployed"), ~ifelse(is.na(.) == TRUE, 0, 1)) %>%
  group_by(time) %>%
  summarize(tig_2 = sum(trust_in_government),
            swd_2 = sum(satisfaction_with_democracy),
            ls_2 = sum(life_satisfaction),
            ue_2 = sum(unemployed)) %>%
  mutate_at(c("tig_2", "swd_2", "ls_2", "ue_2"), ~ifelse(. == 0, "", "-")) %>%
  gather("topic", "value", tig_2:ue_2) %>%
  group_by(topic) %>%
  spread(time, value)

# I create an ordering of rows that will be used in the below table formatting

ordering <- c("tig","swd","ls","ue","tig_2","swd_2","ls_2","ue_2")

# I repeat the steps from LISS for SHP
# Once I have made the table and add the LISS table below
# I arrange by the ordering vector I just made

shp_2<- shp %>%
  select(time, trust_in_government, satisfaction_with_democracy, life_satisfaction, unemployed) %>%
  mutate_at(c("trust_in_government", "satisfaction_with_democracy", "life_satisfaction", "unemployed"), ~ifelse(is.na(.) == TRUE, 0, 1)) %>%
  group_by(time) %>%
  summarize(tig = sum(trust_in_government),
            swd = sum(satisfaction_with_democracy),
            ls = sum(life_satisfaction),
            ue = sum(unemployed)) %>%
  mutate_at(c("tig", "swd", "ls", "ue"), ~ifelse(. == 0, "", "-")) %>%
  gather("topic", "value", tig:ue) %>%
  group_by(topic) %>%
  spread(time, value) %>%
  rbind.fill(liss_2) %>%
  replace(is.na(.), "") %>%
  mutate(topic = factor(topic, levels = ordering)) %>%
  arrange(topic) %>%
  select(-topic)

# Change row names to match those in the paper

row.names(shp_2) <- c("Trust in government (SHP)", "Satisfaction with democracy (SHP", "Life Satisfaction (SHP)", "Employment Status (SHP)", "Trust in government (LISS)", "Satisfaction with democracy (LISS)", "Life Satisfaction (LISS)", "Employment Status (LISS)")

stargazer(
  shp_2,
  header = FALSE,
  summary = FALSE,
  font.size = "small",
  column.sep.width = "-7.5pt",
  title = "Measures across panel waves in the SHP and the LISS"
)
```

```{r table3, results='asis'}

# SHP
# I run six regressions
# Two for each question (trust in government, satisfaction with democracy, and life satisfaction)
# The first regression is just with unemployed as the indenpendent variable
# The second regression includes the controls (age, education, and member)
# The regression uses a pooling technique (plm) to track observations across units (households) 
# over time

shp.fit.pooling.tig <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.ls <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

shp.fit.pooling.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "pooling")

# LISS
# Same as above but with the LISS data instead of the SHP data

liss.fit.pooling.tig <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.ls <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

liss.fit.pooling.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "pooling")

# I display the results using a stargazer table
# I needed to omit the results in the footer like adj.rsq because they were preventing me from 
# adjusting the separation width between columns
# I can't figure out how to add a split header above the dependent variables to separate between 
# SHP and LISS
# I will keep working on this

stargazer(shp.fit.pooling.tig, shp.fit.pooling.control.tig, shp.fit.pooling.swd, shp.fit.pooling.control.swd, shp.fit.pooling.ls, shp.fit.pooling.control.ls, liss.fit.pooling.tig, liss.fit.pooling.control.tig, liss.fit.pooling.swd, liss.fit.pooling.control.swd, liss.fit.pooling.ls, liss.fit.pooling.control.ls,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          column.sep.width = "-7.5pt",
          title = "SHP Switzerland and LISS Netherlands: pooled models",
          column.labels = c("(M1)", "(M2)", "(M3)", "(M4)", "(M5)", "(M6)", "(M7)", "(M8)", "(M9)", "(M10)", "(M11)", "(M12)"), 
          covariate.labels = c("Unemployed", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )

```

```{r table4, results = 'asis'}

# SHP
# The same process as above but I used a fixed effects model instead of a pooled model
# The only difference is I change model from "pooled" to "within"

shp.fit.fe.tig <- plm(trust_in_government ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.ls <- plm(life_satisfaction ~ unemployed, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

shp.fit.fe.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = shp,
                        index = c("unit", "time"),
                        model = "within")

# LISS
# Same as for SHP but with the LISS data

liss.fit.fe.tig <- plm(trust_in_government ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.swd <- plm(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.ls <- plm(life_satisfaction ~ unemployed, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.tig <- plm(trust_in_government ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.swd <- plm(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

liss.fit.fe.control.ls <- plm(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = liss,
                        index = c("unit", "time"),
                        model = "within")

# Stargazer output with the same formatting as Table 3

stargazer(shp.fit.fe.tig, shp.fit.fe.control.tig, shp.fit.fe.swd, shp.fit.fe.control.swd, shp.fit.fe.ls, shp.fit.fe.control.ls, liss.fit.fe.tig, liss.fit.fe.control.tig, liss.fit.fe.swd, liss.fit.fe.control.swd, liss.fit.fe.ls, liss.fit.fe.control.ls,
          omit.stat=c("LL","ser","f","adj.rsq"),
          header = FALSE,
          font.size = "tiny",
          digits = 2,
          label = "table-3",
          column.sep.width = "-7.5pt",
          title = "SHP Switzerland and LISS Netherlands: fixed effects models",
          column.labels = c("(M13)", "(M14)", "(M15)", "(M16)", "(M17)", "(M18)", "(M19)", "(M20)", "(M21)", "(M22)", "(M23)", "(M24)"), 
          covariate.labels = c("Unemployed", "Age", "Education", "Member"),
          dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
          model.names = FALSE,
          model.numbers = FALSE
          )
```

```{r table5calc, include=FALSE}

# SHP
# Same regressions but this time with the weighted fixed effects
# I didn't really understand how these were created so I largely mimicked what Bauer did in his
# replication code

shp.fit.wfe.tig <- wfe(trust_in_government ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.swd <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.ls <- wfe(life_satisfaction ~ unemployed, 
                        data = shp,
                        treat = "unemployed",
                      unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.tig <- wfe(trust_in_government ~ unemployed+ age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.swd <- wfe(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

shp.fit.wfe.control.ls <- wfe(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = shp,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

# LISS
# Same as SHP but with LISS data

liss.fit.wfe.tig <- wfe(trust_in_government ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.swd <- wfe(satisfaction_with_democracy ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.ls <- wfe(life_satisfaction ~ unemployed, 
                        data = liss,
                        treat = "unemployed",
                       unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.tig <- wfe(trust_in_government ~ unemployed+ age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.swd <- wfe(satisfaction_with_democracy ~ unemployed+ age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

liss.fit.wfe.control.ls <- wfe(life_satisfaction ~ unemployed+ age + education  + member, 
                        data = liss,
                        treat = "unemployed",
                        unit.index = "unit", time.index = "time", method = "unit",
               qoi = "ate", estimator =NULL, hetero.se=TRUE, auto.se=TRUE,
               White = TRUE, White.alpha = 0.05, verbose = TRUE)

# The above regressions do not create an output that can be displayed through stargazer
# Instead I needed to manually run the regression with the included weights and then manually
# input those values into stargazer
# Again, I didn't really know how to do this so I just followed what Bauer did.

  regressors <- c("Unemployed", "Age", "Education", "Member")
  d <- as.data.frame(matrix(rnorm(10 * 5), nc = 5))
  dep.var <- "Trust_in_government"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p1 <- lm(f, d)
  dep.var <- "Satisfaction_with_democracy"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p2 <- lm(f, d)
  dep.var <- "Life_satisfaction"
  names(d) <- c(dep.var, regressors)
  f <- as.formula(paste(dep.var, "~ 0 +", paste(regressors, collapse = "+")))
  p3 <- lm(f, d)

```

```{r table5output, results='asis'}

# Stargazer output
# I manually pull out the coefficient values from the regressions and add those to the
# skeleton of the regression that was created above
# I have to do this for each coefficient, each standard error, and each t and p value

# Then I format the stargazer table in the same manner as the previous two

  stargazer(p1, p1, p2, p2, p3, p3, p1, p1, p2, p2, p3, p3,
    coef = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,1]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,1]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,1]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,1])

                ),
    se = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,2]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,2]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,2]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,2])
              ),
    t = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,3]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,3]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,3]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,3])

             ),  
    p = list(as.numeric(summary(shp.fit.wfe.tig)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.tig)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.swd)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.swd)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.ls)[2]$coefficients[,4]),
                as.numeric(summary(shp.fit.wfe.control.ls)[2]$coefficients[,4]),

                as.numeric(summary(liss.fit.wfe.tig)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.tig)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.swd)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.swd)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.ls)[2]$coefficients[,4]),
                as.numeric(summary(liss.fit.wfe.control.ls)[2]$coefficients[,4])
             ),  
    omit.stat = "all",
    notes = "SEs in parentheses.",
    notes.append = TRUE,
    font.size = "tiny",
    digits = 2,
    column.sep.width = "-7.5pt", 
    title = "SHP Switzerland and LISS Netherlands: weighted fixed effects models",
    digit.separator="",
    rownames = FALSE,
    column.labels = c("(M25)", "(M26)", "(M27)", "(M28)", "(M29)", "(M30)", "(M31)", "(M32)", "(M33)", "(M34)", "(M35)", "(M36)"), 
    model.names = FALSE,
    model.numbers = FALSE,
    star.cutoffs=c(0.05,0.01,0.001),
    covariate.labels = c("Unemployed", "Age", "Education", "Member"),
    dep.var.labels = c("trust in government", "statisfaction with democracy", "life satisfaction"),
    header = FALSE)

```

>>>>

---
title: "GOV 1006: Milestone 5"
subtitle: "Paper Replication"
author: "Pieter Quinton"
date: "3/31/2020"
output: 
  bookdown::pdf_document2:
    keep_tex: true
bibliography: milestone5_bib.bib
---

@@

library(stargazer)
library(plyr)
library(tidyverse)
```

The paper I have chosen for my replication project is entitled "Unemployment, Trust in Government, and Satisfaction with Democracy: An Empirical Investigation" (@bauer2018). ^[The replication materials for this paper and my subsequent analyses can be found at my [Github Repo](https://github.com/PGQuinton/gov1006-finalproject-2.0)] It was authored by Paul C. Bauer in 2018. The purpose of the paper is to evaluate how unemployment affects a person's trust in the government and their views towards democracy in general. Bauer begins with macro level data from the Netherlands and Switzerland to construct his analysis but expands to utilize panel data so as to evaluate the relationship on an individual level.

In the below section, I make use of the data collected by Bauer to conduct an analysis on how unemployment, age, and education level affect a person's life satisfaction. I run three regressions, each adding an additional explanatory variable in the above ordering. This is a similar analysis to that conducted in Table 3 of his paper, though I only include the LISS data from The Netherlands. My regressions make use of several packages including the tidyverse, stats, and stargazer (@R-tidyverse; @R-stargazer). The inspiration for my analysis comes from the King et. al. article entitled "Making the Most of Statistical Analyses: Improving Interpretation and Presentation" (@king2000).

```{r, results='asis'}

# Read in the data from the LISS study and save it as data

data <- read_rds("data-long.rds")

# Select the variables I want for my regressions

x <- data %>%
  select(education, age, member, life_satisfaction, unemployed) %>%
  drop_na()

# Run three linear regressions, each time adding another explanatory variable

fit1 <- lm(life_satisfaction ~ unemployed, data = x)

fit2 <- lm(life_satisfaction ~ unemployed + age, data = x)

fit3 <- lm(life_satisfaction ~ unemployed + age + education, data = x)

# Display the results in a singular stargazer table
# Set header to false to hide the commentary from the creator
# Renamed the covariate labels and dependent variable to match the formatting in the paper
# Added a title and source note

stargazer(fit1, fit2, fit3,
          header = FALSE,
          covariate.labels = c("Unemployment", "Age", "Education"),
          dep.var.labels = "Life Satisfaction",
          title = "Effects of Unemployment on Life Satisfaction",
          notes = "Data from Bauer 2018"
          )
```

The results of my regressions confirm the general findings of Bauer. Like he, I also found that unemployment negatively effects a person's life satisfaction. I did not test the effects of unemployment on trust in government and satisfaction in democracy though I will do so in future analyses.

```{r}

@@

```{r, results='asis'}

@@

**The actual table from the paper is below:**

```{r image, out.width="100%"}

# I wasn't sure how to add an image but I found this technique on stackoverflow and seems to
# work well.
# You can set the width of the image in the {r} section above which I did

knitr::include_graphics("milestone5.png")
```

This photo is displayed using a function from the knitr package (@R-knitr).
\newpage
